Bivariate_analysis on different datasets

### 2018-02-08 All_analysis.Rmd
file management

```{r loaddatatest, echo=F}
# here you can directly load the bivariate data to the variable d
# or you can save the bivariate data to d after some data extraction
d<-readRDS("givendata.RDS")
```

@@

```{r loaddata1, echo=F}
# here you can directly load the bivariate data to the variable d
# or you can save the bivariate data to d after some data extraction
d<-readRDS("givendata.RDS")
```

>>>>

```{r loaddatatest, echo=F}
# here you can directly load the bivariate data to the variable d
# or you can save the bivariate data to d after some data extraction
d<-readRDS("../Data/givendata.RDS")
```

@@

```{r loaddata1, echo=F}
# here you can directly load the bivariate data to the variable d
# or you can save the bivariate data to d after some data extraction
d<-readRDS("../Data/givendata.RDS")
```
